\section{Introduction}
\label{sec:introduction}


\subsection{Disposition}
Intro \\
Flat processing schemes vs. deep hierarchies\\
-     paradigm shift \\
PVC deep hierarchy, color \& shape \& receptive field size\\
Fidler intro\\
Compositionality \& bottom-up \& top-down\\
Fidler detail faces and layer structure \\
Discussion \\
-    Compositionality advantages \\
Conclusion \\
Perspective \\
References \\

\todo[inline, author=Jens]{Why is this subject important?
What can we use it for?
Who is it interesting for?
Background}

To realize the vision of continuously expanding human abilities in robotics surely the visual system is of great importance and specifically the task of object recognition is essential to the humanoid robot.

The primate brain's ability to categorize and recognize objects could lead to the idea that the task in its general sense is easy and therefore also easily copied onto an artificial system ie. “Computer vision”. However it is not.
Although the idea of implementing a visual computer system analogue to the biological visual system in the primate brain has existed since the 1970's there is still long way for such a system to be developed. The theories proposed by neuroscientist David Marr \citep{VisualHierarchy} had, until recently been found difficult to implement due to lack of computational power. Hence the main focus in general computer vision has been on designing individual task oriented algorithms that perform analysis and recognition of such features as color shape etc.
The specific task of object recognition through pixel-information might seem easy as the human brain seems to do it instantly and effortlessly. However the seemingly unlimited amount of different objects in addition to variation of size, and posture in the 3D space is a great obstacle in the development of object recognition. Imaging a the simple concept of a cup. As humans we instantly recognize the use of it even when we have never seen that specific type of cup. Size, shape, handle, no handle colour etc.